---
title: "higgs"
author: "YunranChen"
date: "4/1/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	eval = FALSE,
	message = FALSE,
	warning = FALSE,
	include = FALSE
)
setwd("/Users/yunranchen/GoDuke/18Spring/sta650/650project/Higgs Boson")
library(igraph)
library(readr)
library(dplyr)
library(anytime)
library(ggplot2)
library(lubridate)
library(tidyr)
library(purrr)
library(statnet)
#-------------------------------------------------------------------------
theme_set(theme_bw())
#--------------------------------------------------------------------------
#data_total=read_table2(file = "higgs-activity_time.txt",col_names = FALSE,col_types = #cols(X1=col_integer(),X2=col_integer(),X3="?",X4=col_character()))
#colnames(data_total)=c("A","B","ori_time","interact")
#data_total=data_total %>% mutate(time=anytime(ori_time,tz="GMT"),date=anydate(ori_time,tz="GMT"),hour=format(time, format="%Y-%m-%d %H:00:00")%>%anytime(.,tz="GMT"),minute=format(time, format="%Y-%m-%d %H:%M:00")%>%anytime(.,tz="GMT"))
#data_total$interact[data_total$interact=="MT"]="mention"
#data_total$interact[data_total$interact=="RE"]="reply"
#data_total$interact[data_total$interact=="RT"]="retweet"
#save(data_total, file="raw_data.Rdata")
#------------------------------------------------------------------------
load(file="raw_data.Rdata")

```

## number of active users -- time

```{r}

data_act=data_total %>% group_by(hour,interact) %>% summarise(count=n()) 

ggplot(data_act,mapping = aes(x=hour,y=count,linetype=interact,color=interact))+geom_line()+ylab("active account")+xlab("hourly")+geom_vline(xintercept = ("2012-07-04 08:00:00")%>%ymd_hms(.,tz="GMT"))

#data_act=data_total %>% group_by(time) %>% summarise(count=n()) 
#ggplot(data_act,mapping = aes(x=time,y=count))+geom_line()

data_act=data_total %>% mutate(minute_gmt=anytime(minute,tz = "GMT"))%>% group_by(minute,interact) %>% summarise(count=n()) 
ggplot(data_act,mapping = aes(x=minute,y=count,color=interact))+geom_line()+ylab("active account")+xlab("minute")+geom_vline(xintercept = ("2012-07-04 08:00:00")%>%ymd_hms(.,tz="GMT"))

##for science news, retweet is the most popular way for public to express on internet. 

##prevalence: how many people involve in the retweet network : 256491
nodes=data_total[data_total$interact=="retweet",] %>%select (A,B) 
c(nodes$A,nodes$B) %>% unique() %>% length()

##duration: how long it takes to achieve outbreak 1hr55min

rt_data=data_total[data_total$interact=="retweet",]

rt_data%>% group_by(minute) %>% summarise(count=n())%>%arrange(desc(count))%>% .[1,] 



```


## analysis below only consider rt

```{r}
rt_data=data_total[data_total$interact=="retweet",] #flip
rt_data %>% mutate(DateTime=cut(time,breaks = "15 min") %>% anytime(.,tz="GMT"))%>% group_by(DateTime) %>% summarise(count=n())%>% arrange(DateTime) 

```

# dynamic network --time 

## Do not run this chunck

```{r}
#visualization based on every 15 min 
rt_net= rt_data %>% group_by(DateTime=cut(time,breaks = "15 min")%>%anytime(.,tz="GMT")) %>%
  mutate(hm=paste0(hour(DateTime),":",minute(DateTime))) %>% filter(hm=="9:51") %>% 
  select(B,A,DateTime) %>% ungroup()
#net=graph_from_data_frame(rt_net,directed = TRUE)
net_list=split(rt_net,rt_net$DateTime)
net_list_copy=net_list
sl_df=net_list_copy[[4]]
net_list[[4]]=NULL
#p = progress_estimated(length(net_list), min_time = 0)

draw_net=function(df,time_input=0){
net_rt_day=graph_from_data_frame(df[,1:2],directed = TRUE)
  
#Visualization-----------------------------------------------------------------------

#deg <- degree(net_rt_day, mode="out") %>% 
V(net_rt_day)$size <- 3
V(net_rt_day)$label <- NA
V(net_rt_day)$frame.color <- "white"
#V(net_rt_day)$color <- "orange"
# Set edge width based on weight:
#E(net)$width <- E(net)$weight/6

#change arrow size and edge color:
E(net_rt_day)$arrow.size <- .2
E(net_rt_day)$edge.color <- "gray80"
#E(net)$width <- 1+E(net)$weight/12

if (as.logical(time_input)){
  png(filename=paste0(time_input,".png"))
  plot(net_rt_day,layout=layout_with_dh,vertex.color=adjustcolor(col = "orange",alpha.f = .5),main=time_input)
  
}else{
  png(filename=paste0(unique(df$DateTime),".png"))
plot(net_rt_day,layout=layout_with_dh,vertex.color=adjustcolor(col = "orange",alpha.f = .5),main=unique(df$DateTime))
}
dev.off()

}
sapply(net_list,draw_net)
```

```{r}
#visualization based on 40% samples for the network
l_time=net_list_copy[[4]]$DateTime %>% unique()
l_df=l_df %>% select(-DateTime)
hist=l_df %>% group_by(B) %>% summarise(count=n(),prop=ceiling(n()*0.4)) %>% arrange(desc(count))

ss_df=function(i){
s_df=l_df %>% filter(B==as.numeric(hist[i,1])) %>% sample_frac(tbl = .,size =0.4)
return(s_df)
}
s_df=map_df(1:nrow(hist),~ss_df(.x))
hist_s=s_df%>% group_by(B) %>% summarise(count=n(),prop=ceiling(n()*0.4)) %>% arrange(desc(count))
ggplot(hist_s,mapping = aes(x=B,y=count))+geom_line()
draw_net(df = s_df,time_input = l_time)

```

# statistics for each time

##stars;triangles;


```{r}
rt_net= data_total[data_total$interact=="retweet",] %>% select(B,A,hour)
net_list_copy = split(rt_net,rt_net$hour)

summary_net = function(df){
  net_rt_day=graph_from_data_frame(df[,1:2],directed = TRUE)
  density=ecount(net_rt_day)/(vcount(net_rt_day)*(vcount(net_rt_day)-1))
  el_net=get.edgelist(net_rt_day)
  return(c(summary(el_net ~ edges + ostar(2) ),density=density))
}

temp = sapply(net_list_copy,summary_net) %>% t() %>% as.data.frame()
temp = temp %>% mutate(time = rownames(temp))
temp$time = as.POSIXct(temp$time)
library("reshape2")
data_long = melt(temp, id="time")

png(filename="summary.png")
ggplot(data=data_long, aes(x=time, y=value)) + 
  geom_line() + 
  facet_grid(variable~., scales = "free_y") +
  ylab("count") +
  xlab("date")
```

##power-law: the fraction of node with k degree

```{r}
#rt_data = data_total[data_total$interact=="retweet",]
network_total = graph_from_data_frame(rt_data[,c(2,1)],directed = TRUE)

in_dist = degree_distribution(network_total, mode = "in")
in_dist_df = data.frame(degree = 1:length(in_dist), prob = in_dist, type = rep("in", length(in_dist)))

out_dist = degree_distribution(network_total, mode = "out")
out_dist_df = data.frame(degree = 1:length(out_dist), prob = out_dist, type = rep("out", length(out_dist)))

df_total = rbind(in_dist_df, out_dist_df)
df_total$prob = log10(df_total$prob)

png(filename="ispower.png")
ggplot(data=df_total, aes(x=degree, y=prob)) + 
  geom_line() +
  facet_grid(.~type, scales = "free_x") +
  ylab("probabilty") +
  xlab("degree") + 
  scale_y_continuous(breaks=c(0, -2, -4), labels = c(expression(10^0), expression(10^{-2}), expression(10^{-4})))
```

## Density
# The proportion of present edges from all possible ties.

```{r}
library(igraph)
rt_net= data_total[data_total$interact=="retweet",] %>% select(B,A,hour)
net_list_copy = split(rt_net,rt_net$hour)
df=net_list_copy[[1]]
summary_net = function(df){
  net_rt_day=graph_from_data_frame(df[,1:2],directed = TRUE)
  density=ecount(net_rt_day)/(vcount(net_rt_day)*(vcount(net_rt_day)-1))
  centr_closeness=igraph::closeness(net_rt_day, mode="out",weight=NA) 
  centr_eigen=eigen_centrality(net_rt_day, directed=T, weights=NA)
  centr_betweenness=igraph::betweenness(net_rt_day, directed=T, weights=NA)
  return(list(density=density,centr_closeness=centr_closeness,centr_eigen=centr_eigen,
              centr_betweenness=centr_betweenness))
}

temp = sapply(net_list_copy,summary_net) %>% t() %>% as.data.frame()
temp = temp %>% mutate(time = rownames(temp))
temp$time = as.POSIXct(temp$time)
library("reshape2")
data_long = melt(temp, id="time")

png(filename="summary.png")
ggplot(data=data_long, aes(x=time, y=value)) + 
  geom_line() + 
  facet_grid(variable~., scales = "free_y") +
  ylab("count") +
  xlab("date")

```



## Below Network visulization


##follow-up some important node -- using one is enough

##discard some important node -- care about individuals

## Other ways to represent a network -- colorRampPalette degree for color

##http://statnet.csde.washington.edu/workshops/SUNBELT/current/ndtv/ndtv_workshop.html#introduction-to-this-workshop 画个信息图


-------------------------------------------------------------------------------------------------------------

##SIS--hourly

```{r}
#data_social=read_table2(file = "higgs-social_network.edgelist",col_names = FALSE,col_types = cols(X1=col_integer(),X2=col_integer()))
#colnames(data_social)=c("A","B")
#save(data_social, file="data_friendship.Rdata")
#------------------------------------------------------------------------
rt_data=data_total[data_total$interact=="retweet",] 
load(file="data_friendship.Rdata") #followers network
```

```{r}
## get rid of the retweet user.--rt_data_s
rt_data_s=rt_data[!duplicated(rt_data$A),]
#save(rt_data_s, file="data_rt_small.Rdata")
```

```{r}
load(file="data_rt_small.Rdata")
#get the infected number
Is_hourly=rt_data_s%>%group_by(hour,A)%>%summarise(flag=1)%>%select(-flag)
I_n_hourly=Is_hourly%>%ungroup()%>%group_by(hour)%>%summarise(I_n=n())
```


### SIS data -- get rid of the retweet user. +  constant N

```{r}

#set population N as constant
Na=rt_data_s%>%pull(A)%>%unique(.)
Nb=rt_data_s%>%pull(B)%>%unique(.)
N=c(Na,Nb)%>%unique(.)%>%length(.)

SIS_df_s_c=I_n_hourly%>%mutate(I_n=I_n_hourly_ab,S_n=N_social_total-I_n) %>%select(hour,S_n,I_n)
#I_n%>%accumulate(sum)
save(SIS_df_s_c, file="SISdataset_small_consN.Rdata")
SIS_df_s_c_r=I_n_hourly%>%mutate(I_n=I_n_hourly_ab,S_n=N-I_n) %>%select(hour,S_n,I_n)
save(SIS_df_s_c_r, file="SISdataset_small_consN_onlyretweet.Rdata")
```

```{r}
load("SISdataset_small_consN.Rdata")
```

```{r}
load("/Users/yunranchen/GoDuke/18Spring/sta650/650project/Higgs Boson/rstudio-export/pred0.Rdata")
load("/Users/yunranchen/GoDuke/18Spring/sta650/650project/Higgs Boson/rstudio-export/pred1.Rdata")
datadf=SIS_df_s_c%>%mutate(SI_I_n=pred0%>%pull(I_n),SI_S_n=pred0%>%pull(S_n),SIS_I_n=pred1%>%pull(I_n),SIS_S_n=pred1%>%pull(S_n))
SIS_ggdf_s_c=gather(datadf,key = SIS,value = value,-hour)
ggplot(data = SIS_ggdf_s_c,mapping = aes(x = hour,y = value))+geom_line() +facet_grid(SIS~., scales = "free_y")

ggplot(data = SIS_ggdf_s_c,mapping = aes(x = hour,y = value,color=SIS))+geom_line()
```


### SIS data -- get rid of the retweet user. +  inconstant N

```{r}

#get the suspected number: the follower of A are suspected. For A retweet B.
follower_ls=Is_hourly%>%group_by(hour)%>%summarise(list=list(A))%>%pull(list)
flls=follower_ls%>%accumulate(union)
S_hourly_ls=map(.x = follower_ls,.f = ~data_social%>%filter(A%in%.x)%>%pull(B)%>%unique(.))
lls=S_hourly_ls%>%accumulate(union)
#get the suspected number: the follower of B are suspected. For A retweet B.
Is_hourly_b=rt_data_s%>%group_by(hour,B)%>%summarise(flag=1)%>%select(-flag)
follower_ls_b=Is_hourly_b%>%group_by(hour)%>%summarise(list=list(B))%>%pull(list)
flls_b=follower_ls_b%>%accumulate(union) #infected list for B
S_hourly_ls_b=map(.x = follower_ls_b,.f = ~data_social%>%filter(A%in%.x)%>%pull(B)%>%unique(.))
lls_b=S_hourly_ls_b%>%accumulate(union) #suspected list for B


nhrs=length(lls)
Slls_ab_total=map(1:nhrs,~union(lls[[.x]],lls_b[[.x]]))
flls_ab_total=map(1:nhrs,~union(flls[[.x]],flls_b[[.x]])) #accumulated infected list
Slls=map(1:nhrs,~setdiff(Slls_ab_total[[.x]],flls_ab_total[[.x]])) #accumulated suspected list
S_n_hourly=map_dbl(.x = Slls,.f = ~length(.x))
I_n_hourly_ab=map_dbl(.x = flls_ab_total,.f = ~length(.x))

#SIS dataframe
SIS_df_s_ic=I_n_hourly%>%mutate(I_n=I_n%>%accumulate(sum),S_n=S_n_hourly,I_n_ab=I_n_hourly_ab)%>%select(-I_n)
SIS_df_s_ic
#save(SIS_df_s_ic, file="SISdataset_small_inconsN.Rdata")

```

```{r}
load("SISdataset_small_inconsN.Rdata")
```

```{r}
SIS_ggdf_s_ic=gather(SIS_df_s_ic,key = SIS,value = value,-hour)
ggplot(data = SIS_ggdf_s_ic,mapping = aes(x = hour,y = value))+geom_line() +facet_grid(SIS~., scales = "free_y")

ggplot(data = SIS_ggdf_s_ic,mapping = aes(x = hour,y = value,color=SIS))+geom_line()
```

### SIS data -- get rid of the retweet user. +  constant N + memoryless

```{r}

#get the suspected number: the follower of A are suspected. For A retweet B.
follower_ls=Is_hourly%>%group_by(hour)%>%summarise(list=list(A))%>%pull(list)

S_n_hourly=map_dbl(.x = follower_ls,.f = ~data_social%>%filter(A%in%.x)%>%pull(B)%>%setdiff(.,.x)%>%unique(.)%>%length(.))

#SIS dataframe
SIS_df_s_ic_ml=I_n_hourly%>%mutate(S_n=S_n_hourly)
SIS_df_s_ic_ml
#save(SIS_df_s_ic_ml, file="SISdataset_small_inconsN_memoryless.Rdata")

```

```{r}
load("SISdataset_small_inconsN_memoryless.Rdata")
```

```{r}
SIS_ggdf_s_ic_ml=gather(SIS_df_s_ic_ml,key = SIS,value = value,-hour)
ggplot(data = SIS_ggdf_s_ic_ml,mapping = aes(x = hour,y = value))+geom_line() +facet_grid(SIS~., scales = "free_y")

ggplot(data = SIS_ggdf_s_ic_ml,mapping = aes(x = hour,y = value,color=SIS))+geom_line()
```

##SEIZ--hourly

```{r}
load(file="data_friendship.Rdata") #followers network
load(file="data_rt_small.Rdata") #rt network

#get the infected number
Is_hourly=rt_data_s%>%group_by(hour,A)%>%summarise(flag=1)%>%select(-flag)
I_n_hourly=Is_hourly%>%ungroup()%>%group_by(hour)%>%summarise(I_n=n())
#get the suspected number: the follower of A are suspected. For A retweet B.
follower_ls=Is_hourly%>%group_by(hour)%>%summarise(list=list(A))%>%pull(list)
flls=follower_ls%>%accumulate(union) #all infected A list
S_hourly_ls=map(.x = follower_ls,.f = ~data_social%>%filter(A%in%.x)%>%pull(B)%>%unique(.))
lls=S_hourly_ls%>%accumulate(union) #all infected A's followers list
#get the suspected number: the follower of B are suspected. For A retweet B.
Is_hourly_b=rt_data_s%>%group_by(hour,B)%>%summarise(flag=1)%>%select(-flag)
follower_ls_b=Is_hourly_b%>%group_by(hour)%>%summarise(list=list(B))%>%pull(list)
flls_b=follower_ls_b%>%accumulate(union) #infected list for B
S_hourly_ls_b=map(.x = follower_ls_b,.f = ~data_social%>%filter(A%in%.x)%>%pull(B)%>%unique(.))
lls_b=S_hourly_ls_b%>%accumulate(union) #suspected list for B
#Combine the suspected from a and b. infected from a and b
nhrs=length(lls)
Slls_ab_total=map(1:nhrs,~union(lls[[.x]]%>%unique(.),lls_b[[.x]]%>%unique(.))) #accumulated infected list's followers
flls_ab_total=map(1:nhrs,~union(flls[[.x]]%>%unique(.),flls_b[[.x]]%>%unique(.))) #accumulated infected list
Sflls_ab_total=map(1:nhrs,~union(Slls_ab_total[[.x]],flls_ab_total[[.x]])) #accumulated infected and their friends
Slls=map(1:nhrs,~setdiff(Slls_ab_total[[.x]],flls_ab_total[[.x]])) #accumulated suspected list
S_n_hourly=map_dbl(.x = Slls,.f = ~length(.x))
I_n_hourly_ab=map_dbl(.x = flls_ab_total,.f = ~length(.x))

###I:retweet at time t accumulated (has retweeted)
I_n_hourly_ab
###S:has not heard about the news yet
A_social=data_social%>%pull(A)%>%unique(.)
B_social=data_social%>%pull(B)%>%unique(.)
list_total=union(A_social,B_social) #all the people heard the news eventually
N_social_total=list_total%>%length(.)
S_n_hourly_ab=map_dbl(.x=Sflls_ab_total,.f = ~setdiff(list_total,.x)%>%unique(.)%>%length(.))
###Z:has heard but choose not to retweet it
Na=rt_data_s%>%pull(A)%>%unique(.)
Nb=rt_data_s%>%pull(B)%>%unique(.)
I_and_follower_total_ls=union(Na,Nb) #all the people tweet about it
Z_n_hourly_ab=map_dbl(.x = Slls,.f = ~setdiff(.x,I_and_follower_total_ls)%>%unique(.)%>%length(.))
###E:has received the news but take time to tweet
list_total_not=setdiff(list_total,I_and_follower_total_ls) #heard the news but never retweet
E_n_hourly_ab=map_dbl(.x = Slls,.f = ~setdiff(.x,list_total_not)%>%unique(.)%>%length(.))

#SEIZ dataframe
SEIZ_df_s_ic=I_n_hourly%>%mutate(S_n=S_n_hourly_ab,E_n=E_n_hourly_ab,I_n=I_n_hourly_ab,Z_n=Z_n_hourly_ab,N=sum(S_n+E_n+I_n+Z_n))
SEIZ_df_s_ic%>%select(-N,-hour)%>%as.matrix(.)%>%apply(.,1,sum)

SIS_ggdf_s_ic_ml=gather(SEIZ_df_s_ic%>%select(-N),key = SIS,value = value,-hour)
ggplot(data = SIS_ggdf_s_ic_ml,mapping = aes(x = hour,y = value))+geom_line() +facet_grid(SIS~., scales = "free_y")

ggplot(data = SIS_ggdf_s_ic_ml,mapping = aes(x = hour,y = value,color=SIS))+geom_line()

save(SEIZ_df_s_ic, file="SEIZdataset_small_inconsN.Rdata")
load(file = "SEIZdataset_small_inconsN.Rdata")
```

##Result_SI

```{r}
load("SISdataset_small_consN_onlyretweet.Rdata")
load("rstudio-export/retweet_SI.Rdata")
#load("rstudio-export/SI_retweet.Rdata")

rt_df_res=SIS_df_s_c_r%>%mutate(SI_I_n=retweet_SI%>%pull(I_n),SI_S_n=retweet_SI%>%pull(S_n))
rt_ggdf_res=gather(rt_df_res,key = key,value = value,-hour)%>%mutate(State="S",Model="Estimate")
rt_ggdf_res[(rt_ggdf_res%>%pull(key)=="I_n")|(rt_ggdf_res%>%pull(key)=="SI_I_n"),"State"]="I"
rt_ggdf_res[(rt_ggdf_res%>%pull(key)=="I_n")|(rt_ggdf_res%>%pull(key)=="S_n"),"Model"]="True"
rt_ggdf_res

##Result_SIS

err_s=((rt_df_res%>%pull(S_n))-(rt_df_res%>%pull(SI_S_n)))^2 %>% mean(.)
r2_s=err_s/((rt_df_res%>%pull(S_n))^2%>%mean(.))
r2_s%>%format(.,digits=3)
err_i=((rt_df_res%>%pull(I_n))-(rt_df_res%>%pull(SI_I_n)))^2 %>% mean(.)
r2_i=err_i/((rt_df_res%>%pull(I_n))^2%>%mean(.))
r2_i

png(filename="SI_rt_res.png")
ggplot(data = rt_ggdf_res,mapping = aes(x = hour,y = value,color=State,linetype=Model))+geom_line()+annotate("text", x = ("2012-07-07 02:00:00")%>%ymd_hms(.,tz="GMT"), y = 200000, label = paste0("Error_I=",r2_i%>%format(.,digits=3)))+annotate("text", x = ("2012-07-07 02:00:00")%>%ymd_hms(.,tz="GMT"), y = 175000, label = paste0("Error_S=",r2_s%>%format(.,digits=3)))+annotate("text", x = ("2012-07-07 02:00:00")%>%ymd_hms(.,tz="GMT"), y = 150000, label = paste0(as.expression("Beta="),0.1141115%>%format(.,digits=3)))
dev.off()

#beta for SI & retweet: 0.1141115

```

##Result_SIS

```{r}
#beta for SI & whole network: 0.07813026
#alpha, beta for SIS & whole network: 4.657006e+04 2.171945e-01

a=load("SISdataset_small_consN.Rdata")
load("rstudio-export/pred0.Rdata")
load("rstudio-export/pred1.Rdata")

rt_df_res=SIS_df_s_c%>%mutate(SIS_I_n=pred1%>%pull(I_n),SIS_S_n=pred1%>%pull(S_n))
rt_ggdf_res=gather(rt_df_res,key = key,value = value,-hour)%>%mutate(State="S",Model="SIS_Estimate")
rt_ggdf_res[(rt_ggdf_res%>%pull(key)=="I_n")|(rt_ggdf_res%>%pull(key)=="SI_I_n")|(rt_ggdf_res%>%pull(key)=="SIS_I_n"),"State"]="I"
#rt_ggdf_res[(rt_ggdf_res%>%pull(key)=="I_n")|(rt_ggdf_res%>%pull(key)=="S_n"),"SI"]="True"
rt_ggdf_res[(rt_ggdf_res%>%pull(key)=="I_n")|(rt_ggdf_res%>%pull(key)=="S_n"),"Model"]="True"

rt_ggdf_res



##Result_SIS

err_s=((rt_df_res%>%pull(S_n))-(rt_df_res%>%pull(SIS_S_n)))^2 %>% mean(.)
r2_s=err_s/((rt_df_res%>%pull(S_n))^2%>%mean(.))
r2_s
err_i=((rt_df_res%>%pull(I_n))-(rt_df_res%>%pull(SIS_I_n)))^2 %>% mean(.)
r2_i=err_i/((rt_df_res%>%pull(I_n))^2%>%mean(.))
r2_i

png(filename="SIS_nt_res.png")
ggplot(data = rt_ggdf_res,mapping = aes(x = hour,y = value,color=State,linetype=Model))+geom_line()+annotate("text", x = ("2012-07-07 02:00:00")%>%ymd_hms(.,tz="GMT"), y = 200000, label = paste0("Error_I=",r2_i%>%format(.,digits=3)))+annotate("text", x = ("2012-07-07 02:00:00")%>%ymd_hms(.,tz="GMT"), y = 175000, label = paste0("Error_S=",r2_s%>%format(.,digits=3)))+annotate("text", x = ("2012-07-07 02:00:00")%>%ymd_hms(.,tz="GMT"), y = 150000, label = paste0(as.expression("Beta="),2.171945e-01%>%format(.,digits=3)))+
  annotate("text", x = ("2012-07-07 02:00:00")%>%ymd_hms(.,tz="GMT"), y = 125000, label = paste0(as.expression("Alpha="),4.657006e+04%>%format(.,digits=3)))
dev.off()


rt_df_res=SIS_df_s_c%>%mutate(SI_I_n=pred0%>%pull(I_n),SI_S_n=pred0%>%pull(S_n))
rt_ggdf_res=gather(rt_df_res,key = key,value = value,-hour)%>%mutate(State="S",Model="SI_Estimate")
rt_ggdf_res[(rt_ggdf_res%>%pull(key)=="I_n")|(rt_ggdf_res%>%pull(key)=="SI_I_n"),"State"]="I"
rt_ggdf_res[(rt_ggdf_res%>%pull(key)=="I_n")|(rt_ggdf_res%>%pull(key)=="S_n"),"Model"]="True"
#rt_ggdf_res[(rt_ggdf_res%>%pull(key)=="I_n")|(rt_ggdf_res%>%pull(key)=="S_n"),"SIS"]="True"

rt_ggdf_res



##Result_SIS

err_s=((rt_df_res%>%pull(S_n))-(rt_df_res%>%pull(SI_S_n)))^2 %>% mean(.)
r2_s=err_s/((rt_df_res%>%pull(S_n))^2%>%mean(.))
r2_s
err_i=((rt_df_res%>%pull(I_n))-(rt_df_res%>%pull(SI_I_n)))^2 %>% mean(.)
r2_i=err_i/((rt_df_res%>%pull(I_n))^2%>%mean(.))
r2_i

png(filename="SIS_nt_res.png")
ggplot(data = rt_ggdf_res,mapping = aes(x = hour,y = value,color=State,linetype=Model))+geom_line()+annotate("text", x = ("2012-07-07 02:00:00")%>%ymd_hms(.,tz="GMT"), y = 200000, label = paste0("Error_I=",r2_i%>%format(.,digits=3)))+annotate("text", x = ("2012-07-07 02:00:00")%>%ymd_hms(.,tz="GMT"), y = 175000, label = paste0("Error_S=",r2_s%>%format(.,digits=3)))+annotate("text", x = ("2012-07-07 02:00:00")%>%ymd_hms(.,tz="GMT"), y = 150000, label = paste0(as.expression("Beta="),0.07813026%>%format(.,digits=3)))
dev.off()


```

#SEIZ

```{r}
SEIZ_df_s_ic%>%select(-hour,-N)%>%as.matrix()%>%apply(.,1,sum)
a=load("rstudio-export/SEIZ_pred_final!.Rdata")

test=SEIZ_pred%>%as_tibble(.)%>%mutate(hour=SEIZ_df_s_ic%>%pull(hour))
SIS_ggdf_s_ic_ml=gather(SEIZ_pred%>%as_tibble(.),key = SIS,value = value,-hour)
ggplot(data = SIS_ggdf_s_ic_ml,mapping = aes(x = hour,y = value))+geom_line() +facet_grid(SIS~., scales = "free_y")

ggplot(data = SIS_ggdf_s_ic_ml,mapping = aes(x = hour,y = value,color=SIS))+geom_line()


rt_df_res=SEIZ_df_s_ic%>%mutate(SEIZ_I_n=SEIZ_pred%>%pull(I_n),SEIZ_S_n=SEIZ_pred%>%pull(S_n),SEIZ_E_n=SEIZ_pred%>%pull(E_n),SEIZ_Z_n=SEIZ_pred%>%pull(Z_n))%>%select(-N)
rt_ggdf_res=gather(rt_df_res,key = key,value = value,-hour)%>%mutate(State="S",Model="SEIZ_Estimate")
rt_ggdf_res[(rt_ggdf_res%>%pull(key)=="I_n")|(rt_ggdf_res%>%pull(key)=="SEIZ_I_n"),"State"]="I"
rt_ggdf_res[(rt_ggdf_res%>%pull(key)=="E_n")|(rt_ggdf_res%>%pull(key)=="SEIZ_E_n"),"State"]="E"
rt_ggdf_res[(rt_ggdf_res%>%pull(key)=="Z_n")|(rt_ggdf_res%>%pull(key)=="SEIZ_Z_n"),"State"]="Z"
rt_ggdf_res[(rt_ggdf_res%>%pull(key)=="I_n")|(rt_ggdf_res%>%pull(key)=="S_n")|(rt_ggdf_res%>%pull(key)=="E_n")|(rt_ggdf_res%>%pull(key)=="Z_n"),"Model"]="True"
rt_ggdf_res

##Result_SIS

err_s=((rt_df_res%>%pull(S_n))-(rt_df_res%>%pull(SEIZ_S_n)))^2 %>% mean(.)
r2_s=err_s/((rt_df_res%>%pull(S_n))^2%>%mean(.))
r2_s
err_i=((rt_df_res%>%pull(I_n))-(rt_df_res%>%pull(SEIZ_I_n)))^2 %>% mean(.)
r2_i=err_i/((rt_df_res%>%pull(I_n))^2%>%mean(.))
r2_i
err_e=((rt_df_res%>%pull(E_n))-(rt_df_res%>%pull(SEIZ_E_n)))^2 %>% mean(.)
r2_e=err_e/((rt_df_res%>%pull(E_n))^2%>%mean(.))
r2_e
err_z=((rt_df_res%>%pull(Z_n))-(rt_df_res%>%pull(SEIZ_Z_n)))^2 %>% mean(.)
r2_z=err_s/((rt_df_res%>%pull(Z_n))^2%>%mean(.))
r2_z

png(filename="SI_rt_res.png")
ggplot(data = rt_ggdf_res,mapping = aes(x = hour,y = value,color=State,linetype=Model))+geom_line()+annotate("text", x = ("2012-07-07 02:00:00")%>%ymd_hms(.,tz="GMT"), y = 400000, label = paste0("Error_I=",r2_i%>%format(.,digits=3)))+annotate("text", x = ("2012-07-07 02:00:00")%>%ymd_hms(.,tz="GMT"), y = 375000, label = paste0("Error_S=",r2_s%>%format(.,digits=3)))+annotate("text", x = ("2012-07-07 02:00:00")%>%ymd_hms(.,tz="GMT"), y = 350000, label = paste0("Error_E=",r2_e%>%format(.,digits=3)))+annotate("text", x = ("2012-07-07 02:00:00")%>%ymd_hms(.,tz="GMT"), y = 325000, label = paste0("Error_Z=",r2_z%>%format(.,digits=3)))+annotate("text", x = ("2012-07-02 02:00:00")%>%ymd_hms(.,tz="GMT"), y = 300000, label = paste0("beta=",-0.35852358%>%format(.,digits=3)))+annotate("text", x = ("2012-07-02 02:00:00")%>%ymd_hms(.,tz="GMT"), y = 275000, label = paste0("b=",0.74996937%>%format(.,digits=3)))+annotate("text", x = ("2012-07-02 02:00:00")%>%ymd_hms(.,tz="GMT"), y = 250000, label = paste0("p=",0.03593720%>%format(.,digits=3)))+annotate("text", x = ("2012-07-02 02:00:00")%>%ymd_hms(.,tz="GMT"), y = 225000, label = paste0("l=",0.11575087%>%format(.,digits=3)))+annotate("text", x = ("2012-07-02 02:00:00")%>%ymd_hms(.,tz="GMT"), y = 200000, label = paste0("rho=",0.14800669%>%format(.,digits=3)))+annotate("text", x = ("2012-07-02 02:00:00")%>%ymd_hms(.,tz="GMT"), y = 175000, label = paste0("rho=",0.01885045%>%format(.,digits=3)))
dev.off()

#beta is -0.35852358, b is 0.74996937, p is 0.03593720, l is 0.11575087, rho is 0.14800669, epsilon is 0.01885045
```

